---
title: "<center>Product Performance Dashboard</center>"
author: "<center><h3>Zoro Product & Analytics</h3></center>"
date: "<center>December 2016</center><br>"
output: html_document
knit: (function(inputFile, encoding) { 
      out_dir <- 'html';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'Product Performance Dashboard December 2016.html')) })
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,message = FALSE,out.width='100%')
options(warn=-1)
options(digits = 2)
library(ggplot2)
library(plotly)
library(zoo)
library(scales)
library(lubridate)

# working directory
setwd("C:/Users/xsxj045/Documents/Reports/SWS & Zoro-only SKUs Tracker/v2 Sep 2016/scripts/Rmd")

# source code
# source('../code.r',local='TRUE')

# load data
load('../history_summ.rdata')

```


```{r prepare columns, include=FALSE}
# period
history_summ$period <- as.character(as.yearmon(history_summ$year + (history_summ$month - 1)/12))
history_summ$period <- factor(history_summ$period, levels = unique(history_summ$period))

# % Skus Sold
history_summ$percSkusSold <- history_summ$skus_sold / history_summ$skus

# Sales per sku per biz day
history_summ$salesPerSkuDay <- history_summ$sales/history_summ$skus/history_summ$busdays

# GP Rate
history_summ$gpRate <- history_summ$gp/history_summ$sales

# Conversion Rate
history_summ$convRate <- history_summ$web_orders/history_summ$views

# Average Sold Item Price
history_summ$avgPrice <- history_summ$sales/history_summ$qty

# Average Qty per Order
history_summ$avgQty <- history_summ$qty/history_summ$orders

# Average Order Value
history_summ$AOV <- history_summ$sales/history_summ$orders

# Percent of Promo Sales
history_summ$percPromo <- history_summ$promo_sales/history_summ$sales

```

```{r prepare parameters, include=FALSE}

today <- date(now())

# month year
mon <- month(today - day(today))
yyyy <- year(today - day(today))

# month year 3 months ago
mon_3prev <- today - day(today) 

```

```{r save, include=FALSE}
# history data
fileName = paste0('data_',yyyy,'_',mon,'.rdata')
filePath = paste0('data/',fileName)
save.image(filePath)

```

-----

## Instructions
1. **Hover** on the graphs to see the numbers by month
2. **Click the legends** to show/hide a series
3. **Drag a rectangle area** in graph to zoom in
4. **Double click** the graph to zoom out

### Notes
1. `Monthly Sales` for December 2016 was under reported for ~$1M due to database issues. 
2. `Conversion Rate` of July 2016 might not be accurate due to some tagging issues in Google Analytics.
3. Starting from Sep 2016, data for `SWS` and `Zoro-only` skus has been pulled using updated queries. 

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>Monthly Sku Counts</h2> </center>

<br>

* Monthly Sku Count for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$skus / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$skus)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sku Count for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$skus / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$skus)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sku Count for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$skus / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$skus)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sku Count for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$skus / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$skus)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sku Count for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$skus / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$skus)^(1/3) - 1)*100)`** MOM over the last three months

```{r Sku Counts}
plot_ly(
    data = history_summ, x = ~period, y = ~skus, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Monthly Sku Count</b>',hoverformat=',.3s',tickformat=',.3s'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)
    
# plot_ly(data = history_summ, x = ~period, y = ~skus,
#         type = 'scatter', mode = 'lines+markers', color = ~grp,
#         line=list(width=4),
#         marker=list(size=10,color='white',line=list(width=4,colors='Set1'))
# )

```

<hr style="height:1px;color:grey;background-color: grey;">

<center> <h2>Percentage of Skus Sold</h2> </center>

<br>

* Percentage of Skus Sold for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$percSkusSold / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$percSkusSold)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Skus Sold for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$percSkusSold / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$percSkusSold)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Skus Sold for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$percSkusSold / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$percSkusSold)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Skus Sold for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$percSkusSold / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$percSkusSold)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Skus Sold for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$percSkusSold / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$percSkusSold)^(1/3) - 1)*100)`** MOM over the last three months

```{r % Skus Sold}
plot_ly(
    data = history_summ, x = ~period, y = ~percSkusSold, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Percentage of Skus Sold</b>',hoverformat='.2%',tickformat = '%'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>Monthly Sales</h2> </center>

<br>

* Monthly Sales for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$sales / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$sales)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sales for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$sales / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$sales)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sales for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$sales / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$sales)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sales for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$sales / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$sales)^(1/3) - 1)*100)`** MOM over the last three months
* Monthly Sales for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$sales / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$sales)^(1/3) - 1)*100)`** MOM over the last three months

```{r Monthly Sales}
plot_ly(
    data = history_summ, x = ~period, y = ~sales, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Monthly Sales</b>',hoverformat='$,.3s',tickformat='$s'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">

<center> <h2>Sales per Sku per Biz Day</h2> </center>

<br>

* Sales per Sku per Biz Day for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$salesPerSkuDay / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$salesPerSkuDay)^(1/3) - 1)*100)`** MOM over the last three months
* Sales per Sku per Biz Day for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$salesPerSkuDay / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$salesPerSkuDay)^(1/3) - 1)*100)`** MOM over the last three months
* Sales per Sku per Biz Day for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$salesPerSkuDay / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$salesPerSkuDay)^(1/3) - 1)*100)`** MOM over the last three months
* Sales per Sku per Biz Day for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$salesPerSkuDay / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$salesPerSkuDay)^(1/3) - 1)*100)`** MOM over the last three months
* Sales per Sku per Biz Day for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$salesPerSkuDay / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$salesPerSkuDay)^(1/3) - 1)*100)`** MOM over the last three months

```{r Sales per Sku per Biz Day}
plot_ly(
    data = history_summ, x = ~period, y = ~salesPerSkuDay, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Sales per Sku per Biz Day</b>',hoverformat='$,.2r',tickformat='$.2r'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>GP Rate</h2> </center>

<br>

* GP Rate for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$gpRate / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$gpRate)^(1/3) - 1)*100)`** MOM over the last three months
* GP Rate for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$gpRate / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$gpRate)^(1/3) - 1)*100)`** MOM over the last three months
* GP Rate for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$gpRate / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$gpRate)^(1/3) - 1)*100)`** MOM over the last three months
* GP Rate for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$gpRate / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$gpRate)^(1/3) - 1)*100)`** MOM over the last three months
* GP Rate for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$gpRate / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$gpRate)^(1/3) - 1)*100)`** MOM over the last three months

```{r GP Rate}
plot_ly(
    data = history_summ, x = ~period, y = ~gpRate, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>GP Rate</b>',hoverformat='.1%',tickformat='%'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>Conversion Rate</h2> </center>

<br>

* Conversion Rate for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$convRate / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$convRate)^(1/3) - 1)*100)`** MOM over the last three months
* Conversion Rate for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$convRate / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$convRate)^(1/3) - 1)*100)`** MOM over the last three months
* Conversion Rate for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$convRate / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$convRate)^(1/3) - 1)*100)`** MOM over the last three months
* Conversion Rate for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$convRate / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$convRate)^(1/3) - 1)*100)`** MOM over the last three months
* Conversion Rate for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$convRate / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$convRate)^(1/3) - 1)*100)`** MOM over the last three months

```{r Conversion Rate}
plot_ly(
    data = history_summ, x = ~period, y = ~convRate, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Conversion Rate</b>',hoverformat='.2%',tickformat='.1%'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>Average Sold Item Price</h2> </center>

<br>

* Average Sold Item Price for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$avgPrice / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$avgPrice)^(1/3) - 1)*100)`** MOM over the last three months
* Average Sold Item Price for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$avgPrice / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$avgPrice)^(1/3) - 1)*100)`** MOM over the last three months
* Average Sold Item Price for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$avgPrice / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$avgPrice)^(1/3) - 1)*100)`** MOM over the last three months
* Average Sold Item Price for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$avgPrice / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$avgPrice)^(1/3) - 1)*100)`** MOM over the last three months
* Average Sold Item Price for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$avgPrice / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$avgPrice)^(1/3) - 1)*100)`** MOM over the last three months

```{r Average Sold Item Price}
plot_ly(
    data = history_summ, x = ~period, y = ~avgPrice, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Average Sold Item Price</b>',hoverformat='$,.3r',tickformat='$,'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>Average Item Quantity per Order</h2> </center>

<br>

* Average Item Quantity per Order for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$avgQty / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$avgQty)^(1/3) - 1)*100)`** MOM over the last three months
* Average Item Quantity per Order for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$avgQty / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$avgQty)^(1/3) - 1)*100)`** MOM over the last three months
* Average Item Quantity per Order for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$avgQty / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$avgQty)^(1/3) - 1)*100)`** MOM over the last three months
* Average Item Quantity per Order for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$avgQty / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$avgQty)^(1/3) - 1)*100)`** MOM over the last three months
* Average Item Quantity per Order for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$avgQty / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$avgQty)^(1/3) - 1)*100)`** MOM over the last three months

```{r Average Item Quantity per Order}
plot_ly(
    data = history_summ, x = ~period, y = ~avgQty, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Average Item Quantity per Order</b>',hoverformat=',.2r',tickformat=''),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>Average Order Value</h2> </center>

<br>

* Average Order Value for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$AOV / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$AOV)^(1/3) - 1)*100)`** MOM over the last three months
* Average Order Value for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$AOV / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$AOV)^(1/3) - 1)*100)`** MOM over the last three months
* Average Order Value for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$AOV / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$AOV)^(1/3) - 1)*100)`** MOM over the last three months
* Average Order Value for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$AOV / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$AOV)^(1/3) - 1)*100)`** MOM over the last three months
* Average Order Value for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$AOV / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$AOV)^(1/3) - 1)*100)`** MOM over the last three months

```{r Average Order Value}
plot_ly(
    data = history_summ, x = ~period, y = ~AOV, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Average Order Value</b>',hoverformat='$,f',tickformat='$,'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```

<hr style="height:1px;color:grey;background-color: grey;">
<center> <h2>Percentage of Promo Sales</h2> </center>

<br>

* Percentage of Promo Sales for `Drop-ship-LTL` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon)$percPromo / subset(history_summ,grp=='Drop-ship-LTL' & year==yyyy & month==mon-3)$percPromo)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Promo Sales for `Drop-ship-parcel` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon)$percPromo / subset(history_summ,grp=='Drop-ship-parcel' & year==yyyy & month==mon-3)$percPromo)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Promo Sales for `Grainger-stocked` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon)$percPromo / subset(history_summ,grp=='Grainger-stocked' & year==yyyy & month==mon-3)$percPromo)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Promo Sales for `SWS` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='SWS' & year==yyyy & month==mon)$percPromo / subset(history_summ,grp=='SWS' & year==yyyy & month==mon-3)$percPromo)^(1/3) - 1)*100)`** MOM over the last three months
* Percentage of Promo Sales for `Zoro-only` items has been growing **`r sprintf('%.1f%%',((subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon)$percPromo / subset(history_summ,grp=='Zoro-only' & year==yyyy & month==mon-3)$percPromo)^(1/3) - 1)*100)`** MOM over the last three months

```{r Percentage of Promo Sales}
plot_ly(
    data = history_summ, x = ~period, y = ~percPromo, 
    type = 'scatter', mode = 'lines+markers', color = ~grp,
    line=list(width=4), 
    marker=list(size=10)
) %>% layout(
    xaxis = list(title=''),
    yaxis = list(title='<b>Percentage of Promo Sales</b>',hoverformat='.1%',tickformat='%'),
    hovermode = 'x',
    legend = list(x = 1, y = 0.5)
)

```
